Temporal Evolution of Flow in Pore-Networks:\\ From Homogenization to Instability

### 2022-03-06 old_files/june14/paper.tex
Updates from Overleaf

Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic,cohen2015mechanisms} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
The boundaries of the pore structure can change dynamically either through erosion or deposition/sedimentation of material. Such heterogeneous changes of the solid structure affect the pore-level fluid flow which in turn affects the dynamical changes to the pore structure. This feedback mechanism along with the initial heterogeneous fluid flow makes it difficult to understand and predict the porous media behavior. Nonetheless, an understanding of the dynamical change is essential to improve any of the porous media applications where the pore network changes over time, including groundwater remediation and precipitation of minerals in rocks~\cite{rad2013pore}, biofilm growth in water filtration, and protective filters \cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, as well as enhanced oil recovery with polymer flooding \cite{lake2014fundamentals,parsa2020origin}, or water-driven erosion \cite{schorghofer2004spontaneous,mahadevan2012flow}.

@@

    \includegraphics[width = 0.45\textwidth]{Fig1.pdf}

@@

\begin{figure}[!h]
    % \centering
    % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
    \includegraphics[width = 0.48\textwidth]{Fig2_.pdf}
    \caption{Erosion in a network of pipes. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the {simulation result at $t=T$ where  $\langle r_{t=T}\rangle=2r_0$ with $r_0 = \langle r_{t=0}\rangle$}. The erosion law is based on Eq. \eqref{eq:erosion-law}  {where $m=1$ and different powers of $n$ correspond to different models of erosion}. {The first, second, and third columns are snapshots of the pore network, the PDF of normalized fluid flux $q/\langle q \rangle$, and  the PDF of normalized radius $r/\langle r\rangle$ at $t=T$, respectively}.} \label{fig:fig2}
\end{figure}
%
%

@@

\begin{figure}[!h]
    % \centering
     \includegraphics[width = 0.45\textwidth]{Fig3.pdf}
    \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig. \ref{fig:fig2} for different powers of $n$ with $m=1$ plotted over time. (b,c) Tubes in series (b) or parallel (c) configuration. 
    The tube radius dynamically change with the erosion law (Eq. \eqref{eq:erosion-law}). When the tubes are in series, for any $m,n$, (b$_1$) the normalized pressure at the middle junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution. 
    When the tubes are in parallel, for (c$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (c$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (c$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs. }\label{fig:fig3}
\end{figure}

@@

\textit{Analysis of generalized model}-- So far we focused on erosion dynamics with $m=1$ (Eq. \eqref{eq:erosion-law}) since it directly corresponds to erosion laws of interest, i.e. an erosion rate with a linear dependence to fluid-flux, velocity, or shear-rate at the walls. Considering $m=2$ in Eq. \eqref{eq:erosion-law}, our model aligns with the transport optimization problem in biological networks~\cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}. Previous works have suggested that in the context of biological transport networks, the network is optimized to minimize its dissipation energy with regards to some constraint (such as constant material or metabolic cost).  Interestingly, the gradient descent method utilized to find the minimal energy configurations maps to Eq. \eqref{eq:erosion-law} with $m=2$, albeit with additional regularizing terms. While under the dynamics we study here erosion will occur indefinitely, in these biological network models a minimal energy configuration exists due to these additional constraints. Nonetheless, the minimal energy configurations manifest a phase transition reminiscent of the one we observe in our model.
To test the role of the parameter $m$ in our model, we simulated the general form of erosion dynamics (Eq. \eqref{eq:erosion-law}).
The simulation results for a randomly initialized network for different powers of $m$ and $n$ are shown in Fig. \ref{fig:fig4}, where each box shows the final snapshot of the network eroded with the corresponding $m$ and $n$.  We further compare the network's simulation result with the prediction of our simplified model for the fate of the network for each pair of $m,n$. The simplified model's prediction is shown using the bounding box color (red for channelization and green for homogenization) in Fig. \ref{fig:fig4} (cf. Fig. S5 in supplementary material showing the heat map for the average change in the order parameter). Additionally, the dashed black line in Fig. \ref{fig:fig4} shows the simplified model's prediction for the boundary between network's transition to homogeneity or channelization (i.e., $m = (n+1)/4$). Although the simplified model is based on the erosion dynamics of two edges in a parallel or series configuration, it still correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.

\begin{figure}[!h]
    \centering
    \includegraphics[width = 0.45\textwidth]{Fig4.pdf}
    \caption{{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq. \eqref{eq:erosion-law}}. The network is randomly initialized with $50\times 50$ randomly distributed pores. The bounding box color shows the prediction of the simplified  model for the fate of the network: homogenization (blue) or channelization (red). The dashed black line shows the transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.}\label{fig:fig4}
\end{figure}

@@

\begin{acknowledgments}
We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery,  Eleni Katifori, and Chris Rycroft
for useful discussions.
\end{acknowledgments}

\bibliography{ref.bib}

\appendix

>>>>

Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature as well as in numerous environmental and industrial applications~\cite{fraggedakis2015flow,sahimi2011flow,schlesinger1999carbon,duduta2011semi,sun2019hierarchical,marbach2016pruning,tero2010rules,alim2013random,heaton2010growth,smith2017multiphase,ferguson2012nonequilibrium}.
The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
The boundaries of the pore structure can change dynamically either through erosion or deposition/sedimentation of material. Such heterogeneous changes of the solid structure affect the pore-level fluid flow which in turn affects the dynamical changes to the pore structure. This feedback mechanism along with the initial heterogeneous fluid flow makes it difficult to understand and predict the porous media behavior. Nonetheless, an understanding of the dynamical change is essential to improve any of the porous media applications where the pore network changes over time, including groundwater remediation and precipitation of minerals in rocks~\cite{rad2013pore}, biofilm growth in water filtration, and protective filters \cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, as well as enhanced oil recovery with polymer flooding \cite{lake2014fundamentals,parsa2020origin}, or water-driven erosion \cite{schorghofer2004spontaneous,mahadevan2012flow}.

@@

    \includegraphics[width = 0.45\textwidth]{./Fig1.pdf}

@@

\begin{figure}[!h]
    % \centering
    % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
    \includegraphics[width = 0.48\textwidth]{./Fig2.pdf}
    \caption{Erosion in a network of pipes. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the {simulation result at $t=T$ where  $\langle r_{t=T}\rangle=2r_0$ with $r_0 = \langle r_{t=0}\rangle$}. The erosion law is based on Eq. \eqref{eq:erosion-law}  {where $m=1$ and different powers of $n$ correspond to different models of erosion}. {The first, second, and third columns are snapshots of the pore network, the PDF of normalized fluid flux $q/\langle q \rangle$, and  the PDF of normalized radius $r/\langle r\rangle$ at $t=T$, respectively}.} \label{fig:fig2}
\end{figure}
%
%

@@

\begin{figure}[!h]
    % \centering
     \includegraphics[width = 0.45\textwidth]{./Fig3.pdf}
    \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig. \ref{fig:fig2} for different powers of $n$ with $m=1$ plotted over time. (b,c) Tubes in series (b) or parallel (c) configuration. 
    The tube radius dynamically change with the erosion law (Eq. \eqref{eq:erosion-law}). When the tubes are in series, for any $m,n$, (b$_1$) the normalized pressure at the middle junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution. 
    When the tubes are in parallel, for (c$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (c$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (c$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs. }\label{fig:fig3}
\end{figure}

@@

\textit{Analysis of generalized Model}-- So far we focused on erosion dynamics with $m=1$ (Eq. \eqref{eq:erosion-law}) since it directly corresponds to erosion laws of interest, i.e. an erosion rate with a linear dependence to fluid-flux, velocity, or shear-rate at the walls. Considering $m=2$ in Eq. \eqref{eq:erosion-law}, our model aligns with the transport optimization problem in biological networks~\cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}. Previous works have suggested that in the context of biological transport networks, the network is optimized to minimize its dissipation energy with regards to some constraint (such as constant material or metabolic cost).  Interestingly, the gradient descent method utilized to find the minimal energy configurations maps to Eq. \eqref{eq:erosion-law} with $m=2$, albeit with additional regularizing terms. While under the dynamics we study here erosion will occur indefinitely, in these biological network models a minimal energy configuration exists due to these additional constraints. Nonetheless, the minimal energy configurations manifest a phase transition reminiscent of the one we observe in our model.
To test the role of the parameter $m$ in our model, we simulated the general form of erosion dynamics (Eq. \eqref{eq:erosion-law}).
The simulation results for a randomly initialized network for different powers of $m$ and $n$ are shown in Fig. \ref{fig:fig4}, where each box shows the final snapshot of the network eroded with the corresponding $m$ and $n$.  We further compare the network's simulation result with the prediction of our simplified model for the fate of the network for each pair of $m,n$. The simplified model's prediction is shown using the bounding box color (red for channelization and green for homogenization) in Fig. \ref{fig:fig4} (cf. Fig. S5 in supplementary material showing the heat map for the average change in the order parameter). Additionally, the dashed black line in Fig. \ref{fig:fig4} shows the simplified model's prediction for the boundary between network's transition to homogeneity or channelization (i.e., $m = (n+1)/4$). Although the simplified model is based on the erosion dynamics of two edges in a parallel or series configuration, it still correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.

\begin{figure}[!h]
    \centering
    \includegraphics[width = 0.45\textwidth]{./Fig4.pdf}
    \caption{{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq. \eqref{eq:erosion-law}}. The network is randomly initialized with $50\times 50$ randomly distributed pores. The bounding box color shows the prediction of the simplified  model for the fate of the network: homogenization (blue) or channelization (red). The dashed black line shows the transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.}\label{fig:fig4}
\end{figure}

@@

\begin{acknowledgments}
We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery and Eleni Katifori for useful discussions.
\end{acknowledgments}

% \bibliography{ref.bib}
% \appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{48}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Fraggedakis}\ \emph {et~al.}(2015)\citenamefont
  {Fraggedakis}, \citenamefont {Kouris}, \citenamefont {Dimakopoulos},\ and\
  \citenamefont {Tsamopoulos}}]{fraggedakis2015flow}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {Fraggedakis}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Kouris}},
  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Dimakopoulos}}, \ and\
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Tsamopoulos}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physics of
  Fluids}\ }\textbf {\bibinfo {volume} {27}},\ \bibinfo {pages} {082102}
  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sahimi}(2011)}]{sahimi2011flow}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Sahimi}},\ }\href@noop {} {\emph {\bibinfo {title} {Flow and transport in
  porous media and fractured rock: from classical methods to modern
  approaches}}}\ (\bibinfo  {publisher} {John Wiley \& Sons},\ \bibinfo {year}
  {2011})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Schlesinger}(1999)}]{schlesinger1999carbon}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~H.}\ \bibnamefont
  {Schlesinger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Science}\ }\textbf {\bibinfo {volume} {284}},\ \bibinfo {pages} {2095}
  (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Duduta}\ \emph {et~al.}(2011)\citenamefont {Duduta},
  \citenamefont {Ho}, \citenamefont {Wood}, \citenamefont {Limthongkul},
  \citenamefont {Brunini}, \citenamefont {Carter},\ and\ \citenamefont
  {Chiang}}]{duduta2011semi}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Duduta}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Ho}}, \bibinfo
  {author} {\bibfnamefont {V.~C.}\ \bibnamefont {Wood}}, \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Limthongkul}}, \bibinfo {author}
  {\bibfnamefont {V.~E.}\ \bibnamefont {Brunini}}, \bibinfo {author}
  {\bibfnamefont {W.~C.}\ \bibnamefont {Carter}}, \ and\ \bibinfo {author}
  {\bibfnamefont {Y.-M.}\ \bibnamefont {Chiang}},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Advanced Energy Materials}\ }\textbf
  {\bibinfo {volume} {1}},\ \bibinfo {pages} {511} (\bibinfo {year}
  {2011})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2019)\citenamefont {Sun},
  \citenamefont {Zhu}, \citenamefont {Baumann}, \citenamefont {Peng},
  \citenamefont {Xu}, \citenamefont {Shakir}, \citenamefont {Huang},\ and\
  \citenamefont {Duan}}]{sun2019hierarchical}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhu}}, \bibinfo
  {author} {\bibfnamefont {D.}~\bibnamefont {Baumann}}, \bibinfo {author}
  {\bibfnamefont {L.}~\bibnamefont {Peng}}, \bibinfo {author} {\bibfnamefont
  {Y.}~\bibnamefont {Xu}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
  {Shakir}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Huang}}, \
  and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Duan}},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Reviews Materials}\
  }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {45} (\bibinfo {year}
  {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Marbach}\ \emph {et~al.}(2016)\citenamefont
  {Marbach}, \citenamefont {Alim}, \citenamefont {Andrew}, \citenamefont
  {Pringle},\ and\ \citenamefont {Brenner}}]{marbach2016pruning}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Marbach}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Alim}},
  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Andrew}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}}, \ and\ \bibinfo
  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
  }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {178103} (\bibinfo
  {year} {2016})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Tero}\ \emph {et~al.}(2010)\citenamefont {Tero},
  \citenamefont {Takagi}, \citenamefont {Saigusa}, \citenamefont {Ito},
  \citenamefont {Bebber}, \citenamefont {Fricker}, \citenamefont {Yumiki},
  \citenamefont {Kobayashi},\ and\ \citenamefont {Nakagaki}}]{tero2010rules}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Tero}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Takagi}},
  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Saigusa}}, \bibinfo
  {author} {\bibfnamefont {K.}~\bibnamefont {Ito}}, \bibinfo {author}
  {\bibfnamefont {D.~P.}\ \bibnamefont {Bebber}}, \bibinfo {author}
  {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \bibinfo {author}
  {\bibfnamefont {K.}~\bibnamefont {Yumiki}}, \bibinfo {author} {\bibfnamefont
  {R.}~\bibnamefont {Kobayashi}}, \ and\ \bibinfo {author} {\bibfnamefont
  {T.}~\bibnamefont {Nakagaki}},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {327}},\ \bibinfo
  {pages} {439} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2013)\citenamefont {Alim},
  \citenamefont {Amselem}, \citenamefont {Peaudecerf}, \citenamefont
  {Brenner},\ and\ \citenamefont {Pringle}}]{alim2013random}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Alim}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Amselem}},
  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Peaudecerf}}, \bibinfo
  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}}, \ and\ \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
  Academy of Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages}
  {13306} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Heaton}\ \emph {et~al.}(2010)\citenamefont {Heaton},
  \citenamefont {L{\'o}pez}, \citenamefont {Maini}, \citenamefont {Fricker},\
  and\ \citenamefont {Jones}}]{heaton2010growth}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~L.}\ \bibnamefont
  {Heaton}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {L{\'o}pez}},
  \bibinfo {author} {\bibfnamefont {P.~K.}\ \bibnamefont {Maini}}, \bibinfo
  {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \ and\ \bibinfo
  {author} {\bibfnamefont {N.~S.}\ \bibnamefont {Jones}},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the Royal Society
  B: Biological Sciences}\ }\textbf {\bibinfo {volume} {277}},\ \bibinfo
  {pages} {3265} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Smith}\ and\ \citenamefont
  {Bazant}(2017)}]{smith2017multiphase}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~B.}\ \bibnamefont
  {Smith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
  {Bazant}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Journal of The Electrochemical Society}\ }\textbf {\bibinfo {volume}
  {164}},\ \bibinfo {pages} {E3291} (\bibinfo {year} {2017})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Ferguson}\ and\ \citenamefont
  {Bazant}(2012)}]{ferguson2012nonequilibrium}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont
  {Ferguson}}\ and\ \bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
  {Bazant}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Journal of The Electrochemical Society}\ }\textbf {\bibinfo {volume}
  {159}},\ \bibinfo {pages} {A1967} (\bibinfo {year} {2012})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Rad}\ \emph {et~al.}(2013)\citenamefont {Rad},
  \citenamefont {Shokri},\ and\ \citenamefont {Sahimi}}]{rad2013pore}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~N.}\ \bibnamefont
  {Rad}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Shokri}}, \ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Sahimi}},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review E}\ }\textbf
  {\bibinfo {volume} {88}},\ \bibinfo {pages} {032404} (\bibinfo {year}
  {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Herzig}\ \emph {et~al.}(1970)\citenamefont {Herzig},
  \citenamefont {Leclerc},\ and\ \citenamefont {Goff}}]{herzig1970flow}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Herzig}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Leclerc}}, \
  and\ \bibinfo {author} {\bibfnamefont {P.~L.}\ \bibnamefont {Goff}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Industrial \&
  Engineering Chemistry}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages}
  {8} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Tien}\ and\ \citenamefont
  {Payatakes}(1979)}]{tien1979advances}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Tien}}\ and\ \bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
  {Payatakes}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {AIChE Journal}\ }\textbf {\bibinfo {volume} {25}},\ \bibinfo {pages} {737}
  (\bibinfo {year} {1979})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Jaisi}\ \emph {et~al.}(2008)\citenamefont {Jaisi},
  \citenamefont {Saleh}, \citenamefont {Blake},\ and\ \citenamefont
  {Elimelech}}]{jaisi2008transport}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
  {Jaisi}}, \bibinfo {author} {\bibfnamefont {N.~B.}\ \bibnamefont {Saleh}},
  \bibinfo {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Blake}}, \ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Elimelech}},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Environmental Science \&
  Technology}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {8317}
  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Carrel}\ \emph {et~al.}(2018)\citenamefont {Carrel},
  \citenamefont {Morales}, \citenamefont {Beltran}, \citenamefont {Derlon},
  \citenamefont {Kaufmann}, \citenamefont {Morgenroth},\ and\ \citenamefont
  {Holzner}}]{carrel2018biofilms}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Carrel}}, \bibinfo {author} {\bibfnamefont {V.~L.}\ \bibnamefont {Morales}},
  \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Beltran}}, \bibinfo
  {author} {\bibfnamefont {N.}~\bibnamefont {Derlon}}, \bibinfo {author}
  {\bibfnamefont {R.}~\bibnamefont {Kaufmann}}, \bibinfo {author}
  {\bibfnamefont {E.}~\bibnamefont {Morgenroth}}, \ and\ \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Holzner}},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Water Research}\ }\textbf {\bibinfo {volume}
  {134}},\ \bibinfo {pages} {280} (\bibinfo {year} {2018})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Seymour}\ \emph {et~al.}(2004)\citenamefont
  {Seymour}, \citenamefont {Gage}, \citenamefont {Codd},\ and\ \citenamefont
  {Gerlach}}]{seymour2004anomalous}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
  {Seymour}}, \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Gage}},
  \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont {Codd}}, \ and\
  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Gerlach}},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
  }\textbf {\bibinfo {volume} {93}},\ \bibinfo {pages} {198103} (\bibinfo
  {year} {2004})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Lake}\ \emph {et~al.}(2014)\citenamefont {Lake},
  \citenamefont {Johns}, \citenamefont {Rossen}, \citenamefont {Pope} \emph
  {et~al.}}]{lake2014fundamentals}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
  {Lake}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Johns}},
  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Rossen}}, \bibinfo
  {author} {\bibfnamefont {G.~A.}\ \bibnamefont {Pope}},  \emph {et~al.},\
  }\bibfield  {booktitle} {\emph {\bibinfo {booktitle} {Fundamentals of
  Enhanced Oil Recovery}},\ }\href@noop {} {\  (\bibinfo {year}
  {2014})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2020)\citenamefont {Parsa},
  \citenamefont {Santanach-Carreras}, \citenamefont {Xiao},\ and\ \citenamefont
  {Weitz}}]{parsa2020origin}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Parsa}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Santanach-Carreras}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Xiao}}, \ and\ \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
  {Weitz}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Physical Review Fluids}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages}
  {022001} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Schorghofer}\ \emph {et~al.}(2004)\citenamefont
  {Schorghofer}, \citenamefont {Jensen}, \citenamefont {Kudrolli},\ and\
  \citenamefont {Rothman}}]{schorghofer2004spontaneous}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Schorghofer}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Jensen}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kudrolli}}, \ and\
  \bibinfo {author} {\bibfnamefont {D.~H.}\ \bibnamefont {Rothman}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Fluid
  Mechanics}\ }\textbf {\bibinfo {volume} {503}},\ \bibinfo {pages} {357}
  (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mahadevan}\ \emph {et~al.}(2012)\citenamefont
